---
title: "Precis Max Weiss"
author: "Max Weiss"
date: "10/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(knitr)
library(kableExtra)
library(lubridate)

twitter <- read_csv("ira_users_csv_hashed") %>%
  mutate(account_creation_date = ymd(account_creation_date))

```


####This is data recently released by Twitter. Twitter removed the 3,841 Twitter accounts included in this dataset because Twitter believed they were linked to the state-backed Russian Internet Research Agency. The dataset includes information about the accounts including follower/following numbers, account descriptions, language used, and date created. A better understanding of this dataset would better aid our understanding of the state-backed Russian campaign to meddle in the 2016 Presidential Election. 
####[Dataset Can Be Found Here](https://about.twitter.com/en_us/values/elections-integrity.html#data)

#

##First Ten Rows of Russian Twitter Data
```{r, echo=FALSE}

twitter_head <- twitter %>%
  select(userid, user_reported_location:account_language) %>%
  head(10)

kable(twitter_head, caption = "Note: 'user_display_name' and 'user_screen_name' columns were dropped for aesthetics") %>%
  kable_styling(bootstrap_options = "striped", font_size = 8.25)

```

##
```{r, echo=FALSE}

twitter %>%
  ggplot(aes(x = account_creation_date)) +
    labs(title = "Frequency of Dates When Russian Twitter Accounts Created") +
    geom_histogram(bins = 120, fill = "light blue", color = "blue")

```

#Average Number of Followers and Number Following
```{r, echo=FALSE}

twitter %>%
  summarize(mean_followers = mean(follower_count),
            median_followers = median(follower_count),
            mean_following = mean(following_count),
            median_following = median(following_count)) %>%
  kable() %>%
    kable_styling(bootstrap_options = "striped", font_size = 10)

```

##Number of Times Different Partisan Words used in User Profile Description
```{r, echo = FALSE}

c(
  c("Trump", sum(str_detect(twitter$user_profile_description, "Trump"), na.rm = TRUE)),
  c("Conservative", sum(str_detect(twitter$user_profile_description, "Conservative"), na.rm = TRUE)),
  c("Republican", sum(str_detect(twitter$user_profile_description, "Republican"), na.rm = TRUE)))

c(
  c("Hillary", sum(str_detect(twitter$user_profile_description, "Hillary"), na.rm = TRUE)),
  c("Liberal", sum(str_detect(twitter$user_profile_description, "Liberal"), na.rm = TRUE)),
  c("Democrat", sum(str_detect(twitter$user_profile_description, "Democrat"), na.rm = TRUE)))

```

##Counts of Account Language
```{r, echo=FALSE}

twitter %>%
  count(account_language) %>%
  kable()

```




